---
title: "Midterm Project EDA"
author: "Jin Yan, Tao Guo, Jiaqi Sun"
date: "2022-11-09"
output:
  pdf_document: default
  html_document: default
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 5)
library(tidyverse)
library(magrittr)
library(readxl)
library(ggplot2)
library(knitr)
library(kableExtra)
```

## Cleaning data

Separate the column of Data Item

```{r , warning=FALSE}
strawb <- read_xlsx("strawberries-2022oct30-a.xlsx",col_names = TRUE)
## separate the Data Item 
strawb2 <- strawb %>% separate(col=`Data Item`,
                               into = c("Strawberries", "items"),
                               sep = "-",
                               fill = "right")
strawb2 %<>% separate(col = `Strawberries`, into = c("Strawberries", "type", "type2"), 
                      sep = ",", fill = "right")
strawb3 <- strawb2 %>% separate(col = `items`, into = c("sale type", "units"), 
                                sep = ",", fill = "right")

strawb4 <- strawb3 %>% select(-c(4, 8:13, 15, 17))
```

1.  Build organic and non organic tibble

```{r }
Domain_organic1 <- grep("organic", 
                       strawb4$Domain, 
                       ignore.case = T)

org_rows1 <- Domain_organic1
strawb_organic <- strawb4 %>% slice(org_rows1, preserve = FALSE)

strawb_non_organic <- strawb4 %>% filter(!row_number() %in% org_rows1)
```

```{r}
strawb_non_organic %<>% pivot_wider(names_from = `units`, values_from = `Value`)
strawb_organic %<>% pivot_wider(names_from = `units`, values_from = `Value`)
```

2.  From non organic, separate the chemical tibble

```{r echo = FALSE}
chem_rows <- grep("BEARING", 
                       strawb_non_organic$type, 
                       ignore.case = T)
chem_rows_1 <- grep("chemical", 
                  strawb_non_organic$Domain, 
                  ignore.case = T)
## chem_rows and chem_row_1 different rows
## firstly I guess the fertilizer in have BEARING is type column, but It is not in Domain 
chem_rows_f <- grep("FERTILIZER", strawb_non_organic$Domain)
intersect(chem_rows_f, chem_rows)
```

```{r}
strawb_chem <- strawb_non_organic %>% slice(chem_rows, preserve = FALSE)
```

## Poison chemical Carbendazim, Bifenthrin, methyl bromide, 1,3-dichloropropene, chloropicrin, Telone

Searching the Poison chemical mentioned in reading

```{r }
#empty
df_carbendazim <- grep("carbendazim", 
                       strawb_chem$`Domain Category`, ignore.case = T)
df_Bifenthrin <- grep("Bifenthrin", 
                       strawb_chem$`Domain Category`, ignore.case = T)
df_methyl_bromide <- grep("methyl bromide", 
                      strawb_chem$`Domain Category`, ignore.case = T)
#empty
df_1_3_dichloropropene <- grep("1,3-dichloropropene", 
                          strawb_chem$`Domain Category`, 
                          ignore.case = T)
df_chloropicrin <- grep("chloropicrin", 
                               strawb_chem$`Domain Category`, ignore.case = T)
## empty
df_Telone <- grep("Telone", 
                        strawb_chem$`Domain Category`, 
                        ignore.case = T)
```

## Tibble for posion chemicals

The carbendazim, 1_3\_dichloropropene, and Telone did not find in table

```{r }
Bifenthrin <- strawb_chem[df_Bifenthrin,]
methyl_bromide <- strawb_chem[df_methyl_bromide,]
dichloropropene <- strawb_chem[df_chloropicrin,]

```

## Total Posion chemicals by State

```{r echo = FALSE}

Posion_chem <- strawb_chem[c(df_Bifenthrin,df_methyl_bromide,df_chloropicrin ),]


```

```{r }
LB <- ifelse(Posion_chem$` MEASURED IN LB`[1:16]=="(D)",0, Posion_chem$` MEASURED IN LB`[1:16])
LB <- as.numeric(LB)
Posion_chem$` MEASURED IN LB` <- LB
Posion_chem %>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))%>% kable(caption = "Total Posion Chemicals Using by State", digits = 3, format.args = list(big.mark = ",")) %>% kable_minimal(full_width = F)
```

### total chemical using by State

```{r}
LB_total <- ifelse(strawb_chem$` MEASURED IN LB`[1:728]=="(D)"|strawb_chem$` MEASURED IN LB`[1:728]=="(NA)"|strawb_chem$` MEASURED IN LB`[1:728]=="(Z)",0,strawb_chem$` MEASURED IN LB`[1:728])
strawb_chem$` MEASURED IN LB` <- as.numeric(LB_total)
strawb_chem%>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))%>%kable(caption = "Total Chemicals Using by State", digits = 3, format.args = list(big.mark = ",")) %>% kable_minimal(full_width = F)
```

## Percentage poison chemicals by State

```{r}
total_rows <- grep("(TOTAL)", 
strawb_chem$`Domain Category`, ignore.case = T)
fertlizer_rows <- grep("FERTILIZER",strawb_chem$`Domain Category`, ignore.case = T)
chem_total <- strawb_chem[c(total_rows,fertlizer_rows),]
```

```{r}
Posion_state <- Posion_chem %>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
chem_state <- chem_total%>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))

Posion_state$Total_LB <- chem_state$LB_sum

percent_posion_state <- Posion_state %>% mutate(Percent_posion = LB_sum/Total_LB)
percent_posion_state %>%kable(caption = "Percentage Poison Chemicals by State", digits = 3, format.args = list(big.mark = ",")) %>% kable_minimal(full_width = F)
```

```{r}
percent_posion_state1 <- percent_posion_state[-4] %>% pivot_longer(c(LB_sum,Total_LB), names_to = "type",values_to = "value")
```

```{r}
ggplot(percent_posion_state1, aes(fill=type, y=log(value+1), x=State)) + 
    geom_bar(position="dodge", stat="identity")+ylab("log scale of Measure in LB")+
  ggtitle("Poison Chemicals and Total Chemicals by State")+
  scale_fill_discrete(labels = c("Poison Chemicals","Total Chemicals"))
```

From this plot, The California high weight of poison chemicals than
other State, the Oregon almost did not use poison chemicals. Although
the Florida use the poison chemicals, they only use about 0.45%. From
percent_posion_state table, over 30 percent chemicals using in CA is
poison chemicals which is risky for human health.

```{r}
Posion_state_per_years <- Posion_chem %>% group_by(State,Year) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
Posion_state_per_years$`State per Year` <- paste(Posion_state_per_years$State, Posion_state_per_years$Year, sep = " ")

ggplot(Posion_state_per_years, aes(x = `State per Year`, y = log(LB_sum)))+geom_bar(stat = "identity")+coord_flip()+ylab("log Pound of Each State Producation per year with Posion Chemicals ")
```

In this Plot, from 2016 to 2021, the poison chemicals application in
California still maintain at very high levels. Compared to California,
the poison chemicals application in Florida is much lower than
California and in 2021 the Florida did not use poison chemicals at all.
Meanwhile, I find the quantity of California strawberry is extremely
higher than others States, based on two plots, so in next I would like
find the proportion of strawberry quantity by State. \## Strawberry
Proportion by State

```{r, warning = TRUE}
strawb5 <- strawb4 %>% pivot_wider(names_from = `units`, values_from = `Value`)
CWT <- ifelse(strawb5$` MEASURED IN CWT`=="(D)",0,strawb5$` MEASURED IN CWT`)
CWT_LB <- as.numeric(CWT)*100
strawb5$` MEASURED IN LB`[1:54]<- CWT_LB
LB_all <- ifelse(strawb5$` MEASURED IN LB`=="(D)"|strawb5$` MEASURED IN LB`=="(Z)"|
         strawb5$` MEASURED IN LB`=="(NA)",0,strawb5$` MEASURED IN LB`)
strawb5$` MEASURED IN LB` <- as.numeric(LB_all)
fresh_rows <-  grep("FRESH MARKET", strawb5$type2, ignore.case = T)
procss_rows <-  grep("PROCESSING", strawb5$type2, ignore.case = T)
strawb5 <- strawb5[-c(fresh_rows,procss_rows),]
total_rows1 <- grep("(TOTAL)", 
strawb5$`Domain Category`, ignore.case = T)
fertlizer_rows <- grep("FERTILIZER",strawb5$`Domain Category`, ignore.case = T)
organic_rows1 <- grep("ORGANIC",strawb5$type, ignore.case = T)
strawb5 <- strawb5[c(total_rows1,fertlizer_rows,organic_rows1),]
strawb5 %>% group_by(State) %>% summarise(LB = sum(` MEASURED IN LB`, na.rm = TRUE))%>%kable(caption = "Total Strawberry Production by State in Pound", digits = 3, format.args = list(big.mark = ",")) %>% kable_minimal(full_width = F)

```

```{r}
total_state_LB <- strawb5 %>% group_by(State) %>% summarise(LB = sum(` MEASURED IN LB`, na.rm = TRUE))
ggplot(total_state_LB, aes(x="", y=LB, fill=State)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+theme_void()+ggtitle("Total Strawberries Production in Pound by State")
```

This Pi plot responds to my previous opinion, in this data sets, the
California produce over 90% Strawberry. From my percentage poison
chemicals by State, there are 20192300 LB strawberry may harm human
health. Therefore, there are at least 6% strawberry produced in
California, which are harmful.

```{r}
ggplot(total_state_LB, aes(x="", y=log(LB), fill=State)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+theme_void()+ggtitle("Total Strawberries Production in Pound by State")
```

This last figure, I log the value of production of strawberry in order
to find the proportion of other State without California. This Pi chart
show the Florida production is relatively higher than other states.
Others production is closes with each others beside California.

```{r}
ggplot(total_state_LB, aes(x=State, y=log(LB))) + 
  geom_bar(stat = "identity") + theme(legend.position="none")
```

```{r, echo=FALSE,results='hide',message=FALSE}
## Start by reading the data
strawb <- read_xlsx("strawberries-2022oct30-a.xlsx",col_names = TRUE)

## Get the column names and index them
cnames <- colnames(strawb)
x <- 1:dim(strawb)[2]

## Column 1 contains two unique values.  
## Retain column 1 -- those values might be needed.
unique(strawb[1])

## Column 2 -- contains the years included in this dataset.
## Keep column 2, of course.
unique(strawb[2])

## Column 3 -- contains the time periods covered by in the dataset.
## There's only one -- years.  No info here.  Drop it
unique(strawb[3])

## Set T as an indicator
T <- NULL

## Collect number of unique rows in each column
for(i in x){T <- c(T, dim(unique(strawb[i]))[1])}

## Use T to select columns to drop -- 
drop_cols <- cnames[which(T == 1)]

## Now, drop the columns with only one unique value.
strawb %<>% select(!all_of(drop_cols))

## Let's arrange the data frame by year and state.
strawb %<>% arrange(Year, State)
```

```{r, echo=FALSE}
#Tidying the data
strawb %<>% separate(col=`Data Item`,
                    into = c("Strawberries", "type", "items", "units"),
                    sep = ",",
                    fill = "right")
```


```{r, echo=FALSE,results='hide',message=FALSE}
#Tibble Organic
type_organic <- grep("organic", 
               strawb$type, 
               ignore.case = T)

Domain_organic <- grep("organic", 
                      strawb$Domain, 
                      ignore.case = T)

org_rows <- intersect(type_organic, Domain_organic)

strawb_organic <- strawb %>% slice(org_rows, preserve = FALSE)

strawb_organic[strawb_organic$type == " ORGANIC - SALES", ]$units = strawb_organic[strawb_organic$type == " ORGANIC - SALES", ]$items


```

```{r, echo=FALSE,results='hide',message=FALSE}
#Tibble Non-Organic
strawb_non_organic <- strawb %>% filter(!row_number() %in% org_rows)

strawb_non_organic[strawb_non_organic$Strawberries == "STRAWBERRIES - PRICE RECEIVED", ]$items = strawb_non_organic[strawb_non_organic$Strawberries == "STRAWBERRIES - PRICE RECEIVED", ]$type
```


```{r, echo=FALSE,results='hide',message=FALSE}
#Tibble Chemical
## the chemical data in the column "type" 
## is in the rows where type = BEARING - Applications

chem_rows <- grep("BEARING - APPLICATIONS", 
                       strawb_non_organic$type, 
                       ignore.case = T)

strawb_chem <- strawb_non_organic %>% slice(chem_rows, preserve = FALSE)
```


```{r,echo = FALSE,results='hide',message=FALSE}
#Tidying the Tibble Chemical
## now clean up the workspace before tackling the three tibbles just created.
rm(x, T, drop_cols, type_organic, Domain_organic, org_rows, chem_rows,
  cnames, i)

  before_cols = colnames(strawb_chem)
  T = NULL
  x = length(before_cols)

   for(i in 1:x){
    b <- length(unlist(strawb_chem[,i] %>% unique()) )
    T <- c(T,b)
   }
    
  drop_cols <- before_cols[which(T == 1)]
  strawb_chem %<>% select(!all_of(drop_cols))
  after_cols = colnames(strawb_chem)

## drop_cols is labeling information
  
  temp1 <- strawb_chem %>% select(units) %>% distinct()
  ## in units rows are either NA or AVG
  
## separate Domain Category at :
  
  strawb_chem %<>% separate(col=`Domain Category`, 
                                    into = c("dc1", "chem_name"),
                                    sep = ":", 
                                    fill = "right")
  
temp1 <- strawb_chem %>% select(chem_name) %>% unique()
length(unlist(temp1))

## first clean it up

aa  <- grep("measured in", 
                    strawb_chem$items, 
                    ignore.case = T)
length(aa)

## so "item" is really units

## are Domain and dc1 the same thing?

sum(strawb_chem$Domain == strawb_chem$dc1) == dim(strawb_chem)[1]

## yes, they are. let's work with dc1. Also, drop State ANSI

strawb_chem %<>% select(Year, State, items, units, dc1, chem_name, Value)

## items should only contain unit names
## rename units to category

strawb_chem %<>% rename(category = units)

## remove "MEASURED IN " 

strawb_chem$items <- str_remove_all(strawb_chem$items, "MEASURED IN ")

## rename items to units
strawb_chem %<>% rename(units = items)

## Do all the dc1 entries begen with "Chemical"?

bb  <- grep("CHEMICAL, ", 
            strawb_chem$dc1, 
            ignore.case = T)
length(bb)
chem <- 1:2112

non_chem_rows <- setdiff(chem, bb)
length(non_chem_rows)

## on let's look at these rows in a tibble

temp1 <- strawb_chem %>% slice(non_chem_rows)

### !! fertilizers  

## keep them -- probably won't use them as alone tibble

fertilizers <- temp1

## now remove "CHEMICAL, " from the entries in the dc1
## and rename the column chem_types

strawb_chem$dc1 <- str_remove_all(strawb_chem$dc1, "CHEMICAL, ")

strawb_chem$dc1 %>% unique()

strawb_chem %<>% rename(chem_types = dc1)

## now fix the chem_name column

## remove the parens

strawb_chem$chem_name <- str_remove_all(strawb_chem$chem_name, "\\(")

strawb_chem$chem_name <- str_remove_all(strawb_chem$chem_name, "\\)")

## separate chem_name and chem_code

strawb_chem %<>% separate(col = chem_name,
                          into = c("chem_name","chem_code"),
                          sep = "=",
                          fill = "right"
                            ) 

## now fill in a label fot NA in the category column
aa <- which(strawb_chem$units == " LB")

bb <- which(is.na(strawb_chem$category))

sum(aa==bb)==length(aa)

strawb_chem$category[bb] = "Total"

rm(aa, after_cols, b, bb, before_cols, drop_cols, i, non_chem_rows, T, x)

```

```{r, echo=FALSE,results='hide',message=FALSE}
#More tidy work to generate columns as "Per Acre", "Average per Acre per Application" and "Average per Acre per Year"
strawb_chem %>% 
  select(-chem_code) %>% 
  pivot_wider(names_from = units, values_from = Value) %>% 
  rename("per Acre" = " LB") %>% 
  rename("Average per Acre per Application" =  " LB / ACRE / APPLICATION") %>% 
  rename("Average per Acre per Year" =  " LB / ACRE / YEAR") -> strawb_chem
```
```{r, echo =FALSE,results='hide',message=FALSE}
#Chemical Investigation
## investigate chemicals commonly used according to "Shopper’s Guide to Pesticides in Produce™" wihch are deadly possions
chemical_num <- length(unique(strawb_chem$chem_name))

#Bifenthrin, 27 results found, possible human carcinogen
bb  <- grep("BIFENTHRIN", 
            strawb_chem$chem_name, 
            ignore.case = T)

bifen <- strawb_chem %>% slice(bb)

#Carbendazim, nothing found, ormone-disrupting fungicide that damages the male reproductive system and that the EU has banned because of safety concerns.
cc <- grep("CARBENDAZIM", 
            strawb_chem$chem_name, 
            ignore.case = T) 

#chloropicrin, 18 results found, The EU has banned it
ch  <- grep("chloropicrin", 
            strawb_chem$chem_name, 
            ignore.case = T)

chloropicrin <- strawb_chem %>% slice(ch)

#methyl bromide, 2 results found,  The most notorious strawberry fumigant
me  <- grep("methyl bromide", 
            strawb_chem$chem_name, 
            ignore.case = T)

methyl <- strawb_chem %>% slice(me)

#1,3-dichloropropene, nothing found,  The EU has banned it
di  <- grep("1,3-dichloropropene", 
            strawb_chem$chem_name, 
            ignore.case = T)

#Telone, nothing found, 1,3-dichloropropene, The EU has banned it
te  <- grep("Telone", 
            strawb_chem$chem_name, 
            ignore.case = T)
```

```{r,echo=FALSE}
#BIFENTHRIN used per acre per application, varied by year and state
bifen %>% 
  filter(`per Acre` > 0) %>% 
  select(Year, State, chem_name, `per Acre`) %>% 
  group_by(Year, State) -> bifen_pa

#BIFENTHRIN used per acre per application, varied by year and state
bifen %>% 
  filter(`Average per Acre per Application` > 0) %>% 
  select(Year, State, chem_name, `Average per Acre per Application`) %>% 
  group_by(Year, State) -> bifen_papa

#BIFENTHRIN used per acre per year
bifen %>% 
  filter(`Average per Acre per Year` > 0) %>% 
  select(Year, State, chem_name, `Average per Acre per Year`) %>% 
  group_by(Year, State) ->bifen_papy

#chloropicrin used per acre, varied by year and state
chloropicrin %>% 
  filter(`per Acre` > 0) %>% 
  select(Year, State, chem_name, `per Acre`) %>% 
  group_by(Year, State) -> chloropicrin_pa

#chloropicrin used per acre per application, varied by year and state
chloropicrin %>% 
  filter(`Average per Acre per Application` > 0) %>% 
  select(Year, State, chem_name, `Average per Acre per Application`) %>% 
  group_by(Year, State) -> chloropicrin_papa

#chloropicrin used per acre per year, varied by year and state
chloropicrin %>% 
  filter(`Average per Acre per Year` > 0) %>% 
  select(Year, State, chem_name,`Average per Acre per Year`) %>% 
  group_by(Year, State) -> chloropicrin_papy

#methyl used per acre per application, varied by year and state
#nothing returned (with footnote)

pa <- rbind(bifen_pa, chloropicrin_pa)
papa <- rbind(bifen_papa, chloropicrin_papa)
papy <- rbind(bifen_papy, chloropicrin_papy)

pois_all <- rbind(bifen_pa,bifen_papa,bifen_papy, chloropicrin_pa, chloropicrin_papa, chloropicrin_papy)

```

```{r,echo=FALSE}
#BIFENTHRIN used per acre per application, varied by year and state
bifen %>% 
  filter(`per Acre` > 0) %>% 
  select(Year, State, chem_name, `per Acre`) %>% 
  group_by(Year, State) -> bifen_pa

#BIFENTHRIN used per acre per application, varied by year and state
bifen %>% 
  filter(`Average per Acre per Application` > 0) %>% 
  select(Year, State, chem_name, `Average per Acre per Application`) %>% 
  group_by(Year, State) -> bifen_papa

#BIFENTHRIN used per acre per year
bifen %>% 
  filter(`Average per Acre per Year` > 0) %>% 
  select(Year, State, chem_name, `Average per Acre per Year`) %>% 
  group_by(Year, State) ->bifen_papy

#chloropicrin used per acre, varied by year and state
chloropicrin %>% 
  filter(`per Acre` > 0) %>% 
  select(Year, State, chem_name, `per Acre`) %>% 
  group_by(Year, State) -> chloropicrin_pa

#chloropicrin used per acre per application, varied by year and state
chloropicrin %>% 
  filter(`Average per Acre per Application` > 0) %>% 
  select(Year, State, chem_name, `Average per Acre per Application`) %>% 
  group_by(Year, State) -> chloropicrin_papa

#chloropicrin used per acre per year, varied by year and state
chloropicrin %>% 
  filter(`Average per Acre per Year` > 0) %>% 
  select(Year, State, chem_name,`Average per Acre per Year`) %>% 
  group_by(Year, State) -> chloropicrin_papy

#methyl used per acre per application, varied by year and state
#nothing returned (with footnote)

pa <- rbind(bifen_pa, chloropicrin_pa)
papa <- rbind(bifen_papa, chloropicrin_papa)
papy <- rbind(bifen_papy, chloropicrin_papy)

pois_all <- rbind(bifen_pa,bifen_papa,bifen_papy, chloropicrin_pa, chloropicrin_papa, chloropicrin_papy)

```

```{r,echo=FALSE,results='hide',message=FALSE}
## investigate chemicals commonly used, wihch are safe ones

#Acibenzolar-S-methyl, 12 found, has little toxicity to mammals with an LD50 of over 2000 mg/kg (rats, oral). However, it can cause moderate eye irritation.
acib  <- grep(" ACIBENZOLAR-S-METHYL ", 
            strawb_chem$chem_name, 
            ignore.case = T)

ACIB <- strawb_chem %>% slice(acib)

#Acetamiprid, 16 found, has been classified by the EPA as “unlikely” to be a human carcinogen.
acet  <- grep(" ACETAMIPRID ", 
            strawb_chem$chem_name, 
            ignore.case = T)

ACET <- strawb_chem %>% slice(acet)

#acequinocyl, 10 found, unlikely to present a risk to consumer health.
aceq  <- grep(" ACEQUINOCYL ", 
            strawb_chem$chem_name, 
            ignore.case = T)

ACEQ <- strawb_chem %>% slice(aceq)

```


## Safe Chemicals
chemicals commonly used, which are safe ones:
"ACIBENZOLAR-S-METHYL" - 12 results,
" ACETAMIPRID " - 16 results,
" ACEQUINOCYL " - 10 results



## Percentage of poison chemicals

chemicals commonly used according to "Shopper’s Guide to Pesticides in Produce™"
which are deadly possion: "Bifenthrin"-27 results, "chloropicrin"-18 results and
"methyl bromide"-2 results
```{r,,message=FALSE}
# load library
library(ggplot2)

# Create test data.
hazardous_chems <- data.frame(
  category=c("Bifenthrin", "chloropicrin", "methyl bromide"),
  count=c(27, 18, 2)
)
 
# Compute percentages
hazardous_chems$fraction <- hazardous_chems$count / sum(hazardous_chems$count)

# Compute the cumulative percentages (top of each rectangle)
hazardous_chems$ymax <- cumsum(hazardous_chems$fraction)

# Compute the bottom of each rectangle
hazardous_chems$ymin <- c(0, head(hazardous_chems$ymax, n=-1))

# Compute label position
hazardous_chems$labelPosition <- (hazardous_chems$ymax + hazardous_chems$ymin) / 2

# Compute a good label
hazardous_chems$label <- paste0(hazardous_chems$category, "\n value: ", hazardous_chems$count)

# Make the plot
ggplot(hazardous_chems, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category)) +
  geom_rect() +
  geom_label( x=3.5, aes(y=labelPosition, label=label), size=4) +
  scale_fill_brewer(palette=4) +
  coord_polar(theta="y") +
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none")
```


The donuts graph shows the percentage each poison takes in all, with Bifen the most, and chloropicrin second, Methyl bromide least.



## How Much of the Poisons are used Per Acre?

```{r, message=FALSE}
library(ggplot2)

pois_all <- rbind(bifen_pa,bifen_papa,bifen_papy, chloropicrin_pa, chloropicrin_papa, chloropicrin_papy)
pois_all %>% 
  group_by(Year, State) %>% 
  filter(`per Acre` != 0) %>% 
   summarise(`Per_acre_ys` = sum(as.numeric(`per Acre`))) -> pois_all_new
```

```{r, message=FALSE,fig.align='left'}
pois_all_new %>% 
  kable(caption = "<b>Table Poison used Per Acre: raw form</b>", digits = 3, format.args = list(big.mark = ",")) %>%   kable_minimal(full_width = F) 
```
<p style="page-break-before:always">

```{r, message=FALSE}
ggplot(pois_all_new, aes(x = Year, y = log(`Per_acre_ys`+1), colour = State)) +
  geom_line() + 
  labs(x = "Year", 
  y = "Log of poisson used per Acre", 
  title ="How Much of the Poisons are used Per Acre?")
```


we know from the graph below that California has been using very high level of poisson per acre with no plans to decrease them, while Florida hasn't been using much per acre and keep decrease the amount of poison.

We would suggest California to decrease the amount of poison using per acre and suggest customers buy strawberries from States other than California.





## How Much of the Poisons are used Per Acre Per Application?

```{r, message=FALSE}
pois_all <- rbind(bifen_pa,bifen_papa,bifen_papy, chloropicrin_pa, chloropicrin_papa, chloropicrin_papy)
pois_all %>% 
  group_by(Year, State) %>% 
  filter(`Average per Acre per Application` != 0) %>% 
   summarise(`Per_acre_pa_ys` = sum(as.numeric(`Average per Acre per Application`))) -> pois_all_papa

```

```{r,, message=FALSE,fig.align='left'}
pois_all_papa %>% 
  kable(caption = "<b>Table Poison used Per Acre Per Application: raw form</b>", digits = 3, format.args = list(big.mark = ",")) %>%
  kable_minimal(full_width = F)  
```




```{r, message=FALSE}
ggplot(pois_all_papa, aes(x = Year, y = `Per_acre_pa_ys`, colour = State)) +
  geom_line() + 
  labs(x = "Year", 
  y = "Poisson used per Acre per Application", 
  title ="How Much of the Poisons are used Per Acre Per Application?")
```


we know from the graph below that California has been using very high level of poison per acre per application but has to decrease them as the time going, while Florida's using of poisson is nearly 0 per acre per application.

We would suggest California to decrease the amount of poison using per acre per application and suggest customers buy strawberries from States other than California.

## How Much of the Poisons are used Per Acre Per Year?
```{r}
pois_all <- rbind(bifen_pa,bifen_papa,bifen_papy, chloropicrin_pa, chloropicrin_papa, chloropicrin_papy)
pois_all %>% 
  group_by(Year, State) %>% 
  filter(`Average per Acre per Year` != 0) %>% 
   summarise(`Per_acre_papy_ys` = sum(as.numeric(`Average per Acre per Year`))) -> pois_all_papy
```

```{r}
pois_all_papy %>% 
  kable(caption = "<b>Table Poison used Per Acre Per Year: raw form</b>", digits = 3, format.args = list(big.mark = ",")) %>%   kable_minimal(full_width = F) 
```

```{r}
ggplot(pois_all_papy, aes(x = Year, y = `Per_acre_papy_ys`, colour = State)) +
  geom_line() + 
  labs(x = "Year", 
  y = "Poisson used per Acre per Year", 
  title ="How Much of the Poisons are used Per Acre Per Year?")
```


we know from the graph below that California has been using very high level of poison per acre per year but
has to decrease them as the time going, while Florida's using of poisson is nearly 0 per acre per year.

We would suggest California to decrease the amount of poison using per acre per year and suggest customers
buy strawberries from States other than California.


## Improvement data sets 
Firstly, too many columns contained NA should be removed, which are useless. Secondly, many different variables contained in same column, which should be separated. Thirdly, total sales value and others are mixed, which are confused to calculation. Fourthly, the sales units are not recorded in same measurement method, which are
difficult to calculate.

## CV problem

```{r}
population_mean=231304956
CV=0.137
SD=population_mean*CV
ci_upper<-population_mean+1.96*SD
ci_lower<-population_mean-1.96*SD
print(ci_upper)
print(ci_lower)
```

Due to the organic strawberries were collected by census, we can
initiative to collect the data of CV and many of other details, but as
for the non-organic strawberries, the method of collect is survey(the
self-reported), the method lack the enough details for CV and other
complete data, also, if ues we change the method collect of survey to
census, there are much of tima and money we need to cost, it is not
worthy,so there is no CV data for non-organic strawberries. As to the
usage of CV, we through the critical value and SD, we can calculate the
confidence interval for organic strawberries: Margin of error(parameter)
= Critical value*standard deviation for population; population mean=
231304956,CV=13.7%,SD=mean*CV
