---
title: "eda615"
author: "Jin Yan"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##data cleanning
```{r}
## The purpose of this R script is to get you started on the
## midterm project. 

library(tidyverse)
library(magrittr)
library(readxl)

## Start by reading the data
strawb <- read_xlsx("~/desktop/MA615/midterm/strawberries-2022oct30-a.xlsx",col_names = TRUE)

## Get the column names and index them
cnames <- colnames(strawb)
x <- 1:dim(strawb)[2]

## Explore data by viewing it in R.  
## Double click the strawb data frame to lauch the view() function.
## The data frame has 1008 rows, so you can't get very far by
## simply scrolling around.  But, you can generate some initial
## questions to help you explore using R functions from the
## tidyverse.  
##
## It looks like some of the columns may be blank or may contain 
## a single unique value.  These columns can be eliminated without 
## losing any information.

## Start by examining the content of the columns

## Column 1 contains two unique values.  
## Retain column 1 -- those values might be needed.
unique(strawb[1])

## Column 2 -- contains the years included in this dataset.
## Keep column 2, of course.
unique(strawb[2])

## Column 3 -- contains the time periods covered by in the dataset.
## There's only one -- years.  No info here.  Drop it
unique(strawb[3])

## you don't have to do this one column at a time.
## Note that the cells of columns that are empty contain NA, so
## the number of unique values in these columns is 1, just 
## like column_3.

## Set T as an indicator
T <- NULL

## Collect number of unique rows in each column
for(i in x){T <- c(T, dim(unique(strawb[i]))[1])}

## Use T to select columns to drop -- 
drop_cols <- cnames[which(T == 1)]

## Now, drop the columns with only one unique value.
strawb %<>% select(!all_of(drop_cols))

## Let's arrange the data frame by year and state.
strawb %<>% arrange(Year, State)


## Look at the strawb data frame again. You can see that the 
## columns need work. The State ANSI column contains a unique
## code for each state. If you need to access US Census data for
## the states, this code will come in handy.

colnames(strawb)

## now look at the `Data Item` column

temp1 <- strawb %>% select(`Data Item`) %>% 
  distinct()

## Look at temp1!  There's a lot going on there.
## In fact, it's at least three columns packed into one.
## Use separate() to split it up

## When you run this code you can see that there are 
## some rows where `Data Item` has 4 comma-separated 
## data items.  Look at the warning on the Console 
## after 

strawb2 <- strawb %>% separate(col=`Data Item`,
                               into = c("Strawberries", "items", "units"),
                               sep = ",",
                               fill = "right")

## try 4 columns

strawb3 <- strawb %>% separate(col=`Data Item`,
                               into = c("Strawberries", "type", "items", "units"),
                               sep = ",",
                               fill = "right")

## That worked. Clean up the dat.

rm(strawb2, strawb3)

strawb %<>% separate(col=`Data Item`,
                     into = c("Strawberries", "type", "items", "units"),
                     sep = ",",
                     fill = "right")

str(strawb$type)
```

##CV problem
```{r}
population_mean=231304956
CV=0.137
SD=population_mean*CV
ci_upper<-population_mean+1.96*SD
ci_lower<-population_mean-1.96*SD
print(ci_upper)
print(ci_lower)
```

Due to the organic strawberries were collected by census, we can initiative to collecte the data of CV and many of other details, but as for the non-organic strawberries, the method of collect is survey(the self-reported), the method lack the enough details for CV and other complete data, also, if ues we change the method collect of survey to census, there are much of tima and money we need to cost, it is not worthy,so there is no CV data for non-organic strawberries. As to the usage of CV, we through the critical value and SD, we can calculate the confidence interval for organic strawberries: Margin of error(parameter) = Critical value*standard deviation for population; population mean= 231304956,CV=13.7%,SD=mean*CV
